\documentclass[twocolumn,10pt]{article}


\usepackage{times}
\usepackage{cite}
\usepackage{multirow}
\usepackage[tight,footnotesize]{subfigure}
%\usepackage{subfig}

\usepackage{url}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\newcommand{\comment}[1]{}
\newcommand{\eat}[1]{}
\usepackage{booktabs, lastpage}

\usepackage{mdframed, fancyvrb}
\usepackage[scaled]{beramono}
\definecolor{boxcolor}{gray}{0.9}
\newmdenv[linecolor=boxcolor, backgroundcolor=boxcolor, skipabove=\parsep, skipbelow=\parsep, innerleftmargin=2pt, innerrightmargin=2pt]{codeblock}

\newcommand{\myparait}[1]{\smallskip\noindent{\em {#1}:}~}
\newcommand{\myparaq}[1]{\medskip\noindent{\bf {#1}?}~}
\newcommand{\mypara}[1]{\medskip\noindent{\bf {#1}:}~}
\newcommand{\myparatight}[1]{\smallskip\noindent{\bf {#1}:}~}

\newcounter{packednmbr}
\newenvironment{packedenumerate}{\begin{list}{\thepackednmbr.}{\usecounter{packednmbr}\setlength{\itemsep}{1pt}\addtolength{\labelwidth}{-5pt}\setlength{\leftmargin}{\labelwidth}\setlength{\listparindent}{\parindent}\setlength{\parsep}{1pt}\setlength{\topsep}{3pt}}}{\end{list}}
\newenvironment{packeditemize}{\begin{list}{$\bullet$}{\setlength{\itemsep}{1pt}\addtolength{\labelwidth}{-5pt}\setlength{\leftmargin}{\labelwidth}\setlength{\listparindent}{\parindent}\setlength{\parsep}{1pt}\setlength{\topsep}{3pt}}}{\end{list}}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,      % false: boxed links; true: colored links
  linkcolor=blue,       % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=cyan,       % color of file links
  urlcolor=red          % color of external links
}

\definecolor{shadecolor}{gray}{0.9}

\frenchspacing
\pagestyle{plain}

\def\ala{{\`{a} la}~}
\def\ie{{i.e.}}
\def\eg{{e.g.}}
\def\etal{{et al.}~}
\def\wrt{{w.r.t.}~}
\def\viz{viz.~}
\def\vs{vs.~}
\def\etc{etc.}


\begin{document}
\title{18731 Spring 2022 Project Final Report\\ Project Title Here} %of \\ Internet Routing Behavior

\author{
  Team Members
}

\maketitle

\begin{abstract}
  Quick 4-5 sentence abstract of the work:
  1. Motivate problem 2. What is known 3. What you propose to do that is different 4. Key ideas/technical contributons  5.  Outcomes
\end{abstract}


\section{Introduction (1 page}

\begin{itemize}
  \item Para 1 what is the broad problem space you are working on
  \item Para 2 what is the sub problem you are working on
  \item Para 3 what is known from the prior work
  \item Para 4 What are the shortcomings of prior work
  \item Para 5 What is your works contribution
  \item Para 6 what are the main ideas/approaches you are taking
  \item Para 7 what has been implemented
  \item Para 8 what are some of the key outcomes/performance reults
\end{itemize}

\section{Background 1 pg}

what’s proposed already? What have others done already? What
did they learn?


taxnomomize prior work and highlight what is new/different in your work vs theirs


\section{Design and Implementation 1-2pg}


What are plausible alternatives you considered?

provide block diagrams of how the system works, what are the interfaces between components

what are the key ideas and technical challenges

how did you implement/prototype said ideas

\section{Evaluation 1-2pgs}

what is your evaluation setup? methodology? metrics of interest?

What did you do  test out the hypotheses? (E.g.
measurements, simulations, constructing code)


What are the key results .


\section{Conclusions  and Limitations 0.25-0.5 pg}

 {
  \footnotesize
  \raggedright
  \bibliographystyle{abbrv}
  \bibliography{draft}
 }

%\appendix
%\input{concerns}

\end{document}

