\documentclass[twocolumn,10pt]{article}


\usepackage{times}
\usepackage{cite}
\usepackage{multirow}
\usepackage[tight,footnotesize]{subfigure}
%\usepackage{subfig}

\usepackage{url}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\newcommand{\comment}[1]{}
\newcommand{\eat}[1]{}
\usepackage{booktabs, lastpage}

\usepackage{mdframed, fancyvrb}
\usepackage[scaled]{beramono}
\definecolor{boxcolor}{gray}{0.9}
\newmdenv[linecolor=boxcolor, backgroundcolor=boxcolor, skipabove=\parsep, skipbelow=\parsep, innerleftmargin=2pt, innerrightmargin=2pt]{codeblock}

\newcommand{\myparait}[1]{\smallskip\noindent{\em {#1}:}~}
\newcommand{\myparaq}[1]{\medskip\noindent{\bf {#1}?}~}
\newcommand{\mypara}[1]{\medskip\noindent{\bf {#1}:}~}
\newcommand{\myparatight}[1]{\smallskip\noindent{\bf {#1}:}~}

\newcounter{packednmbr}
\newenvironment{packedenumerate}{\begin{list}{\thepackednmbr.}{\usecounter{packednmbr}\setlength{\itemsep}{1pt}\addtolength{\labelwidth}{-5pt}\setlength{\leftmargin}{\labelwidth}\setlength{\listparindent}{\parindent}\setlength{\parsep}{1pt}\setlength{\topsep}{3pt}}}{\end{list}}
\newenvironment{packeditemize}{\begin{list}{$\bullet$}{\setlength{\itemsep}{1pt}\addtolength{\labelwidth}{-5pt}\setlength{\leftmargin}{\labelwidth}\setlength{\listparindent}{\parindent}\setlength{\parsep}{1pt}\setlength{\topsep}{3pt}}}{\end{list}}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,      % false: boxed links; true: colored links
  linkcolor=blue,       % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=cyan,       % color of file links
  urlcolor=red          % color of external links
}

\definecolor{shadecolor}{gray}{0.9}

\frenchspacing
\pagestyle{plain}

\def\ala{{\`{a} la}~}
\def\ie{{i.e.}}
\def\eg{{e.g.}}
\def\etal{{et al.}~}
\def\wrt{{w.r.t.}~}
\def\viz{viz.~}
\def\vs{vs.~}
\def\etc{etc.}


\begin{document}
	\title{18731 Spring 2022 Project Proposal\\ Project Title Here} %of \\ Internet Routing Behavior 
	
\author{
Team Members
  }

\maketitle

\begin{abstract}
Quick 4-5 sentence abstract of the work: 1. Motivate problem 2. What is known 3. What you propose to do that is different 4. Expected outcomes
\end{abstract}


\section{Problem Statement}

What is the problem that this project is going to address?
Does it matter: why is the problem important? Who will
benefit when the problem is solved


1-2 paras


\section{Proposal}

What is the basic approach, method, idea or tool that’s
being suggested to solve the problem?

1-2 paras

\section{Hypotheses}

What exactly are the expected effects of the proposed
solution?


What are plausible alternatives? How likely are they?
What’s good and bad about them by comparison with
what’s proposed? What have others done already? What
did they learn? 


1-2 paras
\section{Experiments}

What will be done to test out the hypotheses? (E.g.
measurements, simulations, constructing code). How will this
confirm (or deny) the hypotheses? Why will the
conclusions be believable?


Who will work on this? For how long? What additional
equipment or other resources will be needed ?

1-2 paras


\section{Results}

What will be the outcome of the work ?  How will we know when they are
complete?

What are the measures for success? (E.g. “faster”,
“smaller”, “more available”.) 


1-2 paras

\section{Milestones and Timeline}

 What are the intermediate
milestones? How will we know when they are
complete?

Bulleted list of milestones

\section{Related Work}

What are the key pieces of related work in this space?

1-2 paras for now, eventually you need to flesh it out


%% 0.5
{
\footnotesize
\raggedright
\bibliographystyle{abbrv}
\bibliography{draft}
}

%\appendix
%\input{concerns}

\end{document}

\caption{\sys processes most traffic at the
